SAYCAM preprocessing analyses from bounding box outputs

### 2021-05-25 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
update to help process high conf bbs

## Paths to raw outputs & datafiles
```{r}
# toggle between each of these folders / dataset types
dataset_dir = "/data/op_outputs_per_vid_rds/"; dataset_type = "all_detections"
# dataset_dir = "/data/op_outputs_per_vid_rds_high_conf/"; dataset_type = "high_conf_detections"

@@

   # make sure we only have high conf detectino
   if (dataset_type=='high_conf_detections'){
      this_vid_data <- this_vid_data %>%
         filter(conf_thres==.5)
      assert_that(length(this_vid_data$frame)>0)
   }

    # summarize hands/faces in each video
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, full_face, eye_distance) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name) %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected), num_full_faces = sum(full_face, na.rm=TRUE), avg_eye_distance = mean(eye_distance, na.rm=TRUE))

@@

    # assert that we have actual center face/hands data 
  # check that length of videos without face/hands in center is not equal to the num of videos in dataframe, 
  assert_that(!sum(is.na(all_vid_data$face_and_hands_center))==length(all_vid_data$vid_name))
}
}
}
```

>>>>

## Paths to raw outputs & datafiles
```{r}
# toggle between each of these folders / dataset types
# dataset_dir = "/data/bounding_boxes/"; dataset_type = "all_detections"
dataset_dir = "/data/high_conf_bounding_boxes/"; dataset_type = "high_conf_detections"

@@

   # make sure we only have high conf detectino
   if (dataset_type=='high_conf_detections'){
      this_vid_data <- this_vid_data %>%
         filter(conf_thres==.5)
      # assert_that(length(this_vid_data$frame)>0)
   }

   if (length(this_vid_data$frame)>0){
    # summarize hands/faces in each video
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, full_face, eye_distance) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name) %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected), num_full_faces = sum(full_face, na.rm=TRUE), avg_eye_distance = mean(eye_distance, na.rm=TRUE))

@@

    # assert that we have actual center face/hands data 
  # check that length of videos without face/hands in center is not equal to the num of videos in dataframe, 
  assert_that(!sum(is.na(all_vid_data$face_and_hands_center))==length(all_vid_data$vid_name))
   }
   }
}
}
```
